My title

### 2024-11-29 paper/paper.qmd
fixed issue with simulations and testing sim data and clean data

library(tidyverse)
library(arrow)
library(here)
library(tibble)
library(knitr)
library(modelsummary)
library(broom)
library(marginaleffects)

@@

@@

@@

What to cite:
- cricketdata
- ESPNCricinfo
- Cricsheet
- kable
- knitr
- R
- tidyverse
- ggplot

>>>>

library(tidyverse)
library(arrow)
library(here)
library(tibble)
library(knitr)
library(modelsummary)
library(marginaleffects)

@@

cleaned_data %>% select(!c(ball, innings, match_id)) %>% head()

@@

bowling_batting_role_matchup_boundaries

@@

What to cite:
- cricketdata
- ESPNCricinfo
- Cricsheet
- All tidyverse packages used
